Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-21 paper.qmd
Added new data with new S-curve data generation

<!--UMAP applied for Scurve data-->
```{r}
umap_scurve <- read_rds(file = "data/s_curve/s_curve_umap.rds")

@@

Three views of the true model in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape. (The **langevitour** software is used to view the data with a tour, and the full video is available at (<https://youtu.be/tYATMiSlCXQ>). 
:::

@@

```{r}
training_data_scurve <- read_rds("data/s_curve/s_curve_training.rds")
```

>>>>

<!--UMAP applied for Scurve data-->
```{r}
umap_scurve <- read_rds(file = "data/s_curve/new/s_curve_umap.rds")

@@

Three views of the true model in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/tYATMiSlCXQ>). 
:::

@@

```{r}
training_data_scurve <- read_rds("data/s_curve/scurve_500.rds")
```
